---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# conquestr

The first goal of `conquestr` is to make it easier to import item analysis files produced by the generalised item response modelling software ConQuest (Wu, Adams, Wilson, & Haldane, 2007) into R. Item analysis text files are generated by the ConQuest itanal command (e.g. `itanal >> my_item_analysis_file.itn;`).

Importing ConQuest item analysis files into R does not appear to be available in other packages as far as we are aware.

# Other resources
See [TAM](https://CRAN.R-project.org/package=TAM) if you'd like to do analysis similar to ConQuest within R.

The `R2conquest` function in the [sirt](https://CRAN.R-project.org/package=sirt) package provides functionality for using ConQuest from within R.

The [WrightMap](https://CRAN.R-project.org/package=WrightMap) package also contains various features for working with ConQuest and other IRT packages.

## Installation

You can install `conquestr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("markdly/conquestr")
```

## Example

First load the relevant packages

```{r, message = FALSE}
library(conquestr)
```


Take a ConQuest version 2 item analysis file. An example one is included with `conquestr`:

```{r example}
cq_example_itanal()
```

Use the example file to try out the other functions. The main one is `cq_itanal`:

```{r}
# get the path to the example itanal file that comes with conquestr
fname <- cq_example_itanal(display = FALSE)
fname

# import the itanal as a tibble
df <- cq_itanal(fname)
df
```

You can show only the statistics for each response option using `cq_resp_stats`:

```{r}
cq_resp_stats(df)

```

## References

Wu, M., Adams, R., Wilson, M., & Haldane, S. (2007). ConQuest Version 2: Generalised Item Response Modelling Software.
